Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2015-01-26 Paper/ms.tex
Fixed minor issue with citation

\section{Introduction}
The number of known extrasolar planets has exploded in the last two
decades. This has been driven by improvements in
all of the different techniques used to detect and characterise exoplanets,
including the radial velocity (RV) method \citep[e.g.][]{2012PASJ...64..135S},
the transit method \citep[e.g.]{2014PNAS..11112647B},
and gravitational microlensing
\citep[e.g.][]{2014ApJ...785..155B, 2014ApJ...790...14Y}.

>>>>

\section{Introduction}
The number of known extrasolar planets has exploded in the last two
decades. This has been driven by improvements in
all of the different techniques used to detect and characterise exoplanets,
including the radial velocity (RV) method \citep[e.g.][]{2012PASJ...64..135S},
the transit method \citep[e.g.][]{2014PNAS..11112647B},
and gravitational microlensing
\citep[e.g.][]{2014ApJ...785..155B, 2014ApJ...790...14Y}.
